Categorical Predictor Embeddings in Actuarial Modeling

### 2021-04-03 manuscript/manuscript.Rmd
more fix

With a single hidden layer, this architecture is the simplest nontrivial neural network; without the hidden layer and
corresponding ReLU activation, we would actually recover a GLM structure where the link function is the output 
activation. 
The choice of one for the embedding dimension is also due to simplicity: it is easily interpretable as the 
representation
of each factor level as a point on the real number line, also, the trained embeddings are easily incorporated into a GLM
which we will see in Model 3. In practice, the embedding dimension is a hyperparameter one can tune, for example via
cross validation, and can vary for each variable. However, we also note that the choice of one for the 
embedding output dimension is not an unreasonable one, especially when the cardinalities of the categorical variables
are not unusually large.

>>>>

With a single hidden layer, this architecture is relatively simple; without the hidden layer and
corresponding ReLU activation, we would actually recover a logistic regression structure. 
The choice of one for the embedding dimension is also due to simplicity: it is easily interpretable as the 
representation
of each factor level as a point on the real number line, also, the trained embeddings are easily incorporated into a GLM
which we will see in Model 3. In practice, the embedding dimension is a hyperparameter one can tune, for example via
cross validation, and can vary for each variable. However, we also note that the choice of one for the 
embedding output dimension is not an unreasonable one, especially when the cardinalities of the categorical variables
are not unusually large.
